SDR enhancement by clouds

### 2024-03-14 article/article.Rmd
Commit 2024-03-14 13:12

@@

@@

```{r echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
knitr::include_graphics("../images/daily-12.png")
```

>>>>

Our dataset after the proccesing consists of

total data points `r ST_total$wattGLB.N`
of which CE are `r ST_total$GLB_diff.N_pos`
and `r ST_total$GLB_diff.N_pos`

@@

```{r loadtrends, echo=F, include=T, warning=FALSE, message=FALSE}
dailytrends <- data.table(
  read.csv("~/MANUSCRIPTS/02_enhancement/figures/Daily_trends_byYear.csv"))
dailytrends[DATA == "ST_E_daily"]

```

By computing the mean daily over irradiance for all the CE case, we were able to dirive a trend on the mean CE intensity of .....

Figures\ \ref{fig:CEmeanDaily}

@@

```{r CEmeanDaily, echo=FALSE, fig.cap="Trend of the daily excess energy due to CE"}
knitr::include_graphics("../images/daily-12.png")
```
